---
title: "W_UP_01"
author: "aubrey garcia"
date: "Summer 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$:  There is no difference between the average number of pushups of line can do in 2 minutes, compared to skill players

$H_A$: The average number of pushups done in two minutes by line players is statistically different than that of skill players.


# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

Average # of push ups is numerical variable
Skill is a categorical variable
We predict push ups based on positions, 
Push ups~Position
we will use the Numerical~Cat helper file.


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(pushups~position,data=mydata)
```


The barplot shows that skilled players do more pushups in two minutes than line players can do in two minutes.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

The table shows that on average line players do about 17 pushups for every two minutes and skill players do about 50 pushups for every 50 pushups for every two minutes. 

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The T-Test shows that the p-vaule is 0.000009421, so we reject the null hypothesis. We conclude that there is a statistical difference in the number of pushups a skilled and line player can do in two minutes. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Data from georgtown college football team, that came from line and skill position players doing as many pushups they could in two minutes. We then had a null hypothesis that states   There is no difference between the average number of pushups of line can do in 2 minutes, compared to skill players. However we rejected it with a p-vaule of 0.000009, which was less that 0.05. The table from numerical results also showed that on average skill players did about 17 pushups in about two minutes and skilled players did on average about 50 pushups in two minutes. So We conclude that there is a statistical difference in the number of pushups a skilled and line player can do in two minutes. 

